\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Added relative proportion density section to the diagnostics

@@

##### Density of a bin

Area of a hexagon is defined as $A = \frac{3\sqrt{3}}{2}l^2$ where $l$ is the side length of the hexagon. If we know $a_1$ and $a_2$, $l$ can be computed (see appendix). Therefore, the density of a hexagon grid is computed as $\frac{\sum^{h}_{i=1}n_h}{A}$ and the proportion is $\frac{\sum^{h}_{i=1}n_h}{A \times b}$. The base line proportion is defined as the

@@

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best hexagon bin parameters and thresholds to remove low-density bins. Both (a) and (c) show MSE, against binwidth ($a_1$) and threshold. A good benchmark value for these parameters is when the MSE drops and then flattens out. Three binwidth choices were made: $0.05$, $0.09$, and $0.12$ to investigate. As the binwidth increases, the proportion of non-empty bins also increases. There are two peaks at binwidths $0.09$ and $0.12$. The proportion of densities, calculated as a density with the smallest possible binwidth, decreases and levels off. Binwidths $0.09$ and $0.12$ are favorable choices. Based on the MSE, $0.09$ was chosen as the initial best binwidth for further analysis. There is no need to remove the low-density hexagons because as shown in (b), there is no considerable drop in MSE."
#| label: fig-param-two-curvy
#| out-width: 80%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

>>>>

### Diagnostics

#### Relative proportion density

The area of a hexagon is defined as $A = \frac{3\sqrt{3}}{2}l^2$ where $l$ is the side length of the hexagon. If we know $a_1$ and $a_2$, $l$ can be computed (see appendix). The density of a hexagon grid is calculated as $\frac{\sum^{h}_{i=1}n_h}{A}$ and the proportion is $\frac{\sum^{h}_{i=1}n_h}{A \times b}$. The baseline proportion is the proportion density at the smallest possible value of $a_1$. The relative proportion density is the ratio of the observed proportion density to the baseline proportion density.

@@

@@

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best hexagon bin parameters and thresholds to remove low-density bins. Both (a) and (c) show MSE, against binwidth ($a_1$) and threshold. A good benchmark value for these parameters is when the MSE drops and then flattens out. Three binwidth choices were made: $0.05$, $0.09$, and $0.12$ to investigate. As the binwidth increases, the proportion of non-empty bins also increases. There are two peaks at binwidths $0.09$ and $0.12$. The relative proportion density decreases and levels off. Binwidths $0.05$ is the favorable choices. Based on the MSE, $0.09$ was chosen as the initial best binwidth for further analysis. There is no need to remove the low-density hexagons because as shown in (b), there is no considerable drop in MSE."
#| label: fig-param-two-curvy
#| out-width: 80%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

### 2024-10-07 paper.tex
Added relative proportion density section to the diagnostics

@@

\caption{\label{fig-param-two-curvy}Various plots to help assess best
hexagon bin parameters and thresholds to remove low-density bins. Both
(a) and (c) show MSE, against binwidth (\(a_1\)) and threshold. A good
benchmark value for these parameters is when the MSE drops and then
flattens out. Three binwidth choices were made: \(0.05\), \(0.09\), and
\(0.12\) to investigate. As the binwidth increases, the proportion of
non-empty bins also increases. There are two peaks at binwidths \(0.09\)
and \(0.12\). The proportion of densities, calculated as a density with
the smallest possible binwidth, decreases and levels off. Binwidths
\(0.09\) and \(0.12\) are favorable choices. Based on the MSE, \(0.09\)
was chosen as the initial best binwidth for further analysis. There is
no need to remove the low-density hexagons because as shown in (b),
there is no considerable drop in MSE.}

>>>>

\subsection{Diagnostics}\label{diagnostics}

\subsubsection{Relative proportion
density}\label{relative-proportion-density}

The area of a hexagon is defined as \(A = \frac{3\sqrt{3}}{2}l^2\) where
\(l\) is the side length of the hexagon. If we know \(a_1\) and \(a_2\),
\(l\) can be computed (see appendix). The density of a hexagon grid is
calculated as \(\frac{\sum^{h}_{i=1}n_h}{A}\) and the proportion is
\(\frac{\sum^{h}_{i=1}n_h}{A \times b}\). The baseline proportion is the
proportion density at the smallest possible value of \(a_1\). The
relative proportion density is the ratio of the observed proportion
density to the baseline proportion density.

@@

\caption{\label{fig-param-two-curvy}Various plots to help assess best
hexagon bin parameters and thresholds to remove low-density bins. Both
(a) and (c) show MSE, against binwidth (\(a_1\)) and threshold. A good
benchmark value for these parameters is when the MSE drops and then
flattens out. Three binwidth choices were made: \(0.05\), \(0.09\), and
\(0.12\) to investigate. As the binwidth increases, the proportion of
non-empty bins also increases. There are two peaks at binwidths \(0.09\)
and \(0.12\). The relative proportion density decreases and levels off.
Binwidths \(0.05\) is the favorable choices. Based on the MSE, \(0.09\)
was chosen as the initial best binwidth for further analysis. There is
no need to remove the low-density hexagons because as shown in (b),
there is no considerable drop in MSE.}
